---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "README-"
)
```

[![Travis-CI Build Status](https://travis-ci.org/coatless/dropcli.svg?branch=master)](https://travis-ci.org/coatless/dropcli)[![CRAN_Status_Badge](http://www.r-pkg.org/badges/version/dropcli)](https://cran.r-project.org/package=dropcli)

# `dropcli` - Dropbox CLI support for Linux Machines

The objective of this package is to provide Command Line Interface (CLI) support
within *R* for the Linux version of Dropbox. 

The CLI is provided by Dropbox's [dropbox.py interface](https://www.dropbox.com/en/help/9192) that is only available on Linux. For details, please see [No support for CLI exists on OS X or Windows](http://superuser.com/questions/678925/using-dropbox-from-the-command-line-on-osx).

As a result, all commands are run through:

```{r dropbox_call, eval = FALSE, engine='bash'}
~/dropbox.py <command> <options>
```

Please **note** this package is a work in progress (WIP) and is *not* suitable
for production use or teaching without knowing what is going on.

If you need a package for multiple platforms, please see the [rdrop2](https://github.com/karthik/rdrop2) by [Karthik Ram](https://github.com/karthik/). This package uses Dropbox's WebAPI via OAuth
instead of an operating system specific package. The downside to this approach
is you *must* initiate the push instead of having a background process take care
of it.

# Dropbox CLI Commands

The commands available via the Dropbox CLI are as follows: 

| Command    | Description                                                  |
|------------|--------------------------------------------------------------|
| status     |  get current status of the dropboxd                          |
| throttle   |  set bandwidth limits for Dropbox                            |
| help       |  provide help                                                |
| puburl     |  get public url of a file in your dropbox's public folder    |
| stop       |  stop dropboxd                                               |
| running    |  return whether dropbox is running                           |
| start      |  start dropboxd                                              |
| filestatus |  get current sync status of one or more files                |
| ls         |  list directory contents with current sync status            |
| autostart  |  automatically start dropbox at login                        |
| exclude    |  ignores/excludes a directory from syncing                   |
| lansync    |  enables or disables LAN sync                                |
| sharelink  |  get a shared link for a file in your dropbox                |
| proxy      |  set proxy settings for Dropbox                              |

# Acknowledgement

The seemingly rapid development of this interface was inspired by [Michael Levy's UseR2016 Talk](http://michaellevy.name/blog/useR-talk-on-teaching-R/) ([See the part at 7:20](https://channel9.msdn.com/Events/useR-international-R-User-conference/useR2016/Teaching-R-to-200-people-in-a-week#time=07m20s)) that details live code piping from the instructor's computer.

This alleviated my concerns for students not being able to:

1. See the code being typed during [STAT 385 @ UIUC](http://stat385.thecoatlessprofessor.com/);
2. Type code sufficiently fast;
3. Avoid the sitting five feet from me while checking [Pokemon Go](http://www.pokemon.com/us/pokemon-video-games/pokemon-go/)

The idea Michael presented was very straightforward: **Provide them with a 
direct link to the code file that updates upon ever save.** 

To do that, there are a few things we need:

1. A Linux machine ([No support for CLI exists on OS X or Windows](http://superuser.com/questions/678925/using-dropbox-from-the-command-line-on-osx))
2. RStudio Server (Pro preferred)
3. An obscure Dropbox knowledge base article entitled [How do I force a file or folder to download or render on dropbox.com?](https://www.dropbox.com/en/help/201)
4. `dropcli`

Alternatively, you can use a local Dropbox install and **manually** go through the
process of enabling a Public document shared URL. Though, I found this to be
the easier approach as I run the [STATS@UIUC Online Analytical Environment](https://rstudio.stat.illinois.edu/).

The rest is history... 
