---
title: "Using `dropcli`"
author: "James Joseph Balamuta"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Using dropcli}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

# Overview

This document contains a brief overview of the features of `dropcli` and how
to use these features. First, we discuss software requirements. Secondly, we
address the need to install the software. Third, we address how to use it.
Fourth, we provide a teaching example.

# Package Requirements

In order to use `dropcli`, you must have:

1. Linux based operating system
2. R
3. Dropbox account

Unfortunately, the linux OS requirement is not negotiable. Principally, the CLI provided by Dropbox's [dropbox.py interface](https://www.dropbox.com/en/help/9192) is only available on Linux. For details, please see [No support for CLI exists on OS X or Windows](http://superuser.com/questions/678925/using-dropbox-from-the-command-line-on-osx).

If you need a package for multiple platforms, please see the [rdrop2](https://github.com/karthik/rdrop2) by [Karthik Ram](https://github.com/karthik/). This package uses Dropbox's WebAPI via OAuth
instead of an operating system specific install. The downside to this approach
is you *must* initiate the push instead of having a background process take care
of it.

# Installation

To install Dropbox's [dropbox.py interface](https://www.dropbox.com/en/help/9192),
there are two options:

1. Try using `dropcli`'s `dropcli::install_dropbox_cli()`
2. Follow the guide given at: 
[Dropbox Headless Install](https://www.dropbox.com/install?os=lnx).

## Option 1: Install via R

This process is somewhat automated within R via:

```{r dropbox_r, eval = FALSE}
dropcli::install_dropbox_cli()
```

You will need to copy and paste the URL in your browser to link the dropbox
account with your dropbox.

Then, skip to the **Turn on `autostart`** subsection. 
This immediately follows after Option 2.

## Option 2: Install via Terminal

To install in terminal, we'll need to perform a headless or text-only install.

Dropbox provides a guide for it at: [Dropbox Headless Install](https://www.dropbox.com/install?os=lnx).
However, you may need to resort to using Google's cache to access an up-to-date
copy of the instructions  as Dropbox attempt to automatically detect and serve the
appropriate client to you based on your current operating system.

With that being said, the setup required is as follows:

For 32-bit:

```{r bash_32, eval = F, engine='bash'}
cd ~ && wget -O - "https://www.dropbox.com/download?plat=lnx.x86" | tar xzf -
```

For 64-bit:

```{r bash_64, eval = F, engine='bash'}
cd ~ && wget -O - "https://www.dropbox.com/download?plat=lnx.x86_64" | tar xzf -
```

Then, we launch from shell the Dropbox daemon out of the newly created `.dropbox-dist` folder.

```{r dropboxd, eval = F, engine='bash'}
~/.dropbox-dist/dropboxd
```

Here, you will be prompted to follow a URL. Please do so! Copy and paste it in
your browser.

Next, we'll download the `dropbox.py` interface via:

```{r dropbox_py, eval = F}
wget -O dropbox.py https://www.dropbox.com/download?dl=packages/dropbox.py
```

And voila! We're done with the install.

## Turn on `autostart`!

After the package has been installed, please turn on the `autostart` option.
This makes sure that once the system user is logged in then the dropbox daemon
is automatically running. In turn, this allows for the use of the CLI within R
as the state of the system is destroyed after each call. 

To turn on `autostart` use either:

1. R via `dropcli::dropbox_autostart()`
2. Shell via `~/dropbox.py autostart y`

# Playing with Commands

There are a few helpful commands

| Command    | Description                                                  | `dropcli` Functions    |
|------------|--------------------------------------------------------------|------------------------|
| status     |  get current status of the dropboxd                          | `dropbox_status()`     |
| throttle   |  set bandwidth limits for Dropbox                            |       **MIA**          | 
| help       |  provide help                                                |`dropbox_help(topic)`   |
| puburl     |  get public url of a file in your dropbox's public folder    |`dropbox_puburl(fp)`    |
| stop       |  stop dropboxd                                               |`dropbox_stop()`        |
| running    |  return whether dropbox is running                           |`dropbox_running()`     | 
| start      |  start dropboxd                                              |`dropbox_start()`       |
| filestatus |  get current sync status of one or more files                |`dropbox_filestatus()`  |
| ls         |  list directory contents with current sync status            |      **MIA**           |
| autostart  |  automatically start dropbox at login                        |`dropbox_autostart()`   |
| exclude    |  ignores/excludes a directory from syncing                   |      **MIA**           |
| lansync    |  enables or disables LAN sync                                |      **MIA**           |
| sharelink  |  get a shared link for a file in your dropbox                | `dropbox_sharelink(fp)`|
| proxy      |  set proxy settings for Dropbox                              |      **MIA**           |


# Teaching Example

The seemingly rapid development of this interface was inspired by [Michael Levy's UseR2016 Talk](http://michaellevy.name/blog/useR-talk-on-teaching-R/) ([See the part at 7:20](https://channel9.msdn.com/Events/useR-international-R-User-conference/useR2016/Teaching-R-to-200-people-in-a-week#time=07m20s)) that details live code piping from the instructor's computer.

This alleviated my concerns for students not being able to:

1. See the code being typed during [STAT 385 @ UIUC](http://stat385.thecoatlessprofessor.com/);
2. Type code sufficiently fast;
3. Avoid the sitting five feet from me while checking [Pokemon Go](http://www.pokemon.com/us/pokemon-video-games/pokemon-go/)

The idea presented was very straightforward: **Provide students with a 
direct link to the code file that updates upon every save done by the file editor.** 

To do that, there are a few things we need:

1. A Linux machine ([No support for CLI exists on OS X or Windows](http://superuser.com/questions/678925/using-dropbox-from-the-command-line-on-osx))
2. RStudio Server (Pro preferred)
3. An obscure Dropbox knowledge base article entitled [How do I force a file or folder to download or render on dropbox.com?](https://www.dropbox.com/en/help/201)
4. `dropcli`

Alternatively, you can use a local Dropbox install and **manually** go through the
process of enabling a Public document shared URL. Though, I found this to be
the easier approach as I run the [STATS@UIUC Online Analytical Environment](https://rstudio.stat.illinois.edu/).

With that being said, to generate such a link either:

1. pick a file in the `Public` directory and use:
```{r public_dir, eval = FALSE}
dropcli::dropbox_puburl_live("path/to/Public/file.R")`
```

2. pick a file in the **not** in the `Public` directory and use:
```{r non_public_dir, eval = FALSE}
dropcli::dropbox_sharelink_live("path/to/file.R")`
```

Thus, you now have a shareable link. It doesn't look pretty, but it is shareable.

At a later time, support may be added for using a URL shortener within *R*.

